Spatial Reasoning and Statistical Graphics

### 2014-11-14 Paper/Draft1/TestingVisualAptitude.Rnw
attempt at mean structure with residuals for pca - not sure that it is successful, it seems to be very similar to the other pca

>>>>

<<>>=
vistests <- scale(lineup.section.summary[,c("card_rot", "fig_class", "folding", "vis_search")])
lineups <- scale(lineup.section.summary[,c("lineup_1", "lineup_2", "lineup_3")])
vmain <- rowSums(vistests)/4
alltests <- data.frame(vmain, vistests-vmain, lineups)
pctests <- prcomp(alltests)
biplot(pctests)
biplot(pctests, 3:4)
